Komols Complexity, Coresets, and Sketches in Machine Learning

### 2018-12-30 komlos.tex
reorder and organize

\begin{abstract}
This paper defines the Komlos complexity for families of functions which is intimately related to its discrepancy properties.
We argue that this measure of complexity captures properties like minimal coreset sizes for different problems in machine learning. We show that for many well known problems the Komlos complexity is asymptotically lower than their Rademacher complexity. This proves the existence smaller coresets than those achievable by random sampling. 
New results for coresets for kernel density estimation, matrix covariance approximation, and logistic regression are presented both as examples of for providing mechanisms to compute the Komlos complexity of other classes.
For all of the above we match the state of the art or improve on it.
This makes an explicit connection between low discrepancy, streaming algorithms, coresets, and learnability. 
%We also asymptotically improve on the generic merge-reduce framework for creating mergeable sketches for all the above problems. 
\end{abstract}

@@

In many machine learning and sketching problems our goal is often to approximate the sum (or expectation) of functions.
Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\Q$ which is known in advance. For simplicity and throughout this manuscript we will assume $f:\X\times\Q\rightarrow [0,1]$.
The goal is to produce weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript.

@@

@@

\zk{need to finish the analysis for the above $K_k$..}
\end{proof}

From section \ref{} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$. Here, we show that for any positive kernel $K_m = O(1/\sqrt{m})$. This bound is better when the $d > m$. More importantly though, there is a very simple and deterministic algorithm for computing the signs $\sigma$. 
Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
$$ f(q) = \sum_{i=1}^{n} K(x_i,q) $$
Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
$$ K(x,q) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,q) = \exp(- \|x-q\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-q\|/_2^2/\lambda^2)^{-1}$$
where $\lambda$ is a scaling parameter. For simplicity, we assume that $K(x,x) \leq 1$ for all data points. Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.

Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$. For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
$$ K(x,q) = \ip{\phi(x), \phi(q)} $$
Using this function $\phi$ our objective function becomes
\[
\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| %\leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| 
\]
This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
We will show by induction that $\| \sum_{j=1}^i \sigma_j \phi(x_j) \|^2 \le \sum_{j=1}^i \|\phi(x_j)\|^2$ for all $i$.
This is trivially true for $i=1$. 
For another value assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.

\begin{eqnarray*}
\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)\rangle \\
&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
\end{eqnarray*}
This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$. 
%
%Let us now translate this to an algorithm w.r.t.\ the $d$ dimensional points $x_1,\ldots, x_k$. 
%The sign of $x_1$ is set arbitrarily as $s_1=1$. For $i>1$, we choose 
%$$ \sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j \langle \phi(x_j), \phi(x_i) \rangle) = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$$
%This guarantees that 
%$$ \forall y \in \R^d \;\;\; \sum \sigma_i K(x_i, y) \leq \sqrt{ \sum \|\phi(x_i)\|^2 } = \sqrt{m} $$

Using the framework above this provides a coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde f(q) - f(q)| \le \eps n$. This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.
%\el{The running time of this algorithm is amortized.... I hope it will be better than Jeff's result, especially in the randomized shrinking buffers setting.}
%\zk{We actually ended up using the Radamacher complexity, at least for the bound. Namely, we used random signs. Perhaps there is a kernel for which it is easy to prove something better? One that comes to mind is apx low rank data. By low rank I mean in the kernel space, meaning the $\phi(x_j)$'s. To find the core-set we can first run PCA on the $z_i$'s, reduce their dimension from $n$ to being the minimal such that we suffer a loss of $\eps$. Then, we use theory on the sum of unit vectors of low dimension giving $\sqrt{k}/\eps$ where $k$ is the dimension we got. In the worst case if the kernel matrix is isotropic we will get $k \approx n$ and gain nothing, but this way we can squeeze something from the data that wasn't squeezed before.. We can take this further and look into the details of the proof that we can balance unit vectors to have a norm of $\sqrt{d}$ regardless of the number of vectors. The key in that proof is that by considering continuous $s_i$'s we can have the sum equal to zero while keeping only $d$ points with non $\{-1,1\}$ $s_i$'s. Consider a split of top $k$ and bottom rest directions. If we restrict the $s_i$'s to only have the sum to be zero in the top $k$ we get $k$ non integral $s_i$'s but possibly horrible performance on the bottom $k$. What if only restrict $d-2k$ and not $d-k$ points? Then we get some freedom in choosing the integer $s_i$'s. The bound on the bottom singular values can become smaller than the trivial one.}

\section{Universal Coresets for Analytic Functions of Dot Products}

We are now ready to apply Banaszczyk's theorem. 
There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$.
Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that $\max_k \|\sum_i \sigma_i  x_i^{\otimes k}\|_{T_k} \le \sqrt{d k \log^{3}(k)}$

\begin{lemma} \label{lem:komlos anl}
Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion. The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq 1$, is bounded by
\[
K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) \le \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}
\]
For general $\|q\| \leq R$ we get
\[
K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) \le \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}
\]
\end{lemma}
\begin{proof}
The proof follows from combining the above.
$$
\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \cdot \|q\|^k
$$
By Lemma \ref{uc} we can find signs $\sigma$ such that 
$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
\end{proof}

\begin{theorem}
Let $\tilde{f}$ be an analytical one dimension function over $\R$. There exist a radius $R$ such that for $\|q\| \leq R$ the function family of functions $f_q(x) = \tilde{f}(\ip{q,x})$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d})$ 
\end{theorem}
\begin{proof}
Recall that for analytical functions $f$ we have 
$$\left| \frac{d^k \tilde{f}}{dz^k}(z) \right|  \leq C^{k+1} k! $$
for some constant $C$. Considering the taylor expansion of $\tilde{f}$ near zero we get that for $R < 1/C$, the sum
$$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} \leq C \sum_k  (CR)^k \sqrt{ k\log^3(k)}$$
corresponding to Lemma~\ref{lem:komlos anl} converges to a constant. The result follows.
\end{proof}

\begin{corollary}
The Komlos complexity of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d})$.
\end{corollary}

Notice that by transforming $x$ to $\tilde{x} = (-x, \|x\|^2, 1)$ and $q$ to $\tilde{q} = (q, 1, \|q\|^2)$ we get $\ip{\tilde{x},\tilde{q}} = \|x-q\|^2$. This implies that our results for functions of $\ip{q,x}$ apply for functions of $\|q-x\|^2$. In particular we get
\begin{corollary}
The Komlos complexity of the Gaussian kernel in dimension $d$ is $O(\sqrt{d})$.
\end{corollary}

@@

To invoke Banaszczyk's theorem here we set $x_i \in \R^{d_1d_2}$ to be the flattening of $X_i$ into a vector by concatenating its rows. 
Let $\mathcal K$ be the set of vectors in $\R^{d_1d_2}$ whose stacking (the inverse of flattening) results in a matrix whose spectral norm is less then $c\sqrt{d_1 + d_2}$.
More accurately $\mathcal K = \{x  \in \R^{d_1d_2} |\;\; ||\operatorname{stack}(x)||_2 \le c\sqrt{d_1+d_2}\}$. 
Due to $\operatorname{stack}$ being linear it is obvious that $\mathcal K$ is convex. 
Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices (see Theorem~\ref{thm:random tensor}).
Banaszczyk's theorem says that there exist signs $\sigma_i$ such that $\sum \sigma_i \operatorname{flatten}(X_i) \in C \mathcal K$.
In other words $\| \sum \sigma_i X_i\| = \| \operatorname{stack}( \sum \sigma_i \operatorname{flatten}(x_i x_i^T)) \| \le C \sqrt{d}$. 
\end{proof}
The algorithm for finding the signs above is, unfortunately, not as simple as with kernels. 
In fact, Banaszczyk's theorem was not constructive and a matching algorithms is a very recent breakthrough result by Bansal, Dadush, Garg, and Lovett \cite{DBLP:conf/stoc/BansalDGL18}.

@@

\subsection{Streaming Graph Approximation}
Streaming graphs have received a lot of attention in the last several years \zk{cite something here \cite{}}. 
In the standard setting, the edges of a graph $G(V,E)$ are given to an algorithm one ofter the other in arbitrary order.
Here we show how to approximate all quadratic forms $\sum_{(i,j) \in E} (q_i - q_j)^2$ where the values $q$ are not known in advance.
Let $L_e$ be the graph Laplacian of the edge $e$. More accurately, $L_e(i,i) = L_e(j,j) = 1$ and  $L_e(i,j) = L_e(j,i) = -1$ and all other values are zeros.
Then, $\sum_{(i,j) \in E} (q_i - q_j)^2 = q^T \sum_{e \in E}L_e q = q^T L q$. 
In this formulation, this problem reduced to that of row (column) subset selection. 
Note that $L_e = v_ev_e^T$ where $v_e(i) = 1$, $v_e(j)=-1$ and zero else.
Applying the results of the last section we get a streaming mergeable algorithm of approximating graph quadratic forms.
The number of retained edges in the coreset $E'$ is $|E'| = O(\log^{2}(n) \sqrt{n}/\eps)$ and it guaranties that 
$|\sum_{(i,j) \in E} (q_i - q_j)^2  - c \sum_{(i,j) \in E'} (q_i - q_j)^2| \le \eps n$ for all unit norm vectors $q$.

%\paragraph{Reduction to the Kernel case}
%This is really the Kernel density estimation problem with $K(x,y) = \ip{x,y}^2$. We might be able to squeeze a bit more due to the fact that $\phi(x) = xx^T$ is a very special $d \times d$ matrix: a rank $1$ matrix. That being said, a coreset of $1/\eps^2$ can be obtained by simply using the kernel technique. The special structure can either give better dependence on $\eps$ or exploit low rank structure e.g.\ if the vectors form a nearly rank $k$ matrix.

%
%\subsection{notes about row selection}
%The problem is 
%$$ \min_s \| \sum_i \sigma_i x_ix_i^T\| $$
%where $\|x_i\| \leq 1$. Consider the following greedy approach: At point $x_i$, let
%$$ C_i = \sum_{j<i} \sigma_j x_j x_j^T, \ \  l_+ = \|C_i + x_i x_i^T \|, \ l_- = \|C_i - x_i x_i^T\|$$
%We choose $\sigma_i = 1$ if $l_+ < l_i$, otherwise $\sigma_i=-1$.
%
%This approach can be shown to be better than random. Random will result in an answer of up to 
%
%Consider the following example. 
%$$x_1=e_1, x_2=e_2*\eps, x_3=e_2, x_4=e_1/\sqrt{2} + e_2/\sqrt{2}$$
%where $\eps \to 0$. We get that the covariance matrix after inserting $x_3$ has two eigenvalues of +1 and -1. Now when inserting $x_4$ we have to increase the magnitude of one of them and we exceed the limit of 1. 
%

>>>>

\begin{abstract}
\el{I need to rewrite the abstract}
This paper defines the Komlos complexity for families of functions which is intimately related to its discrepancy properties.
We argue that this measure of complexity captures properties like minimal coreset sizes for different problems in machine learning. We show that for many well known problems the Komlos complexity is asymptotically lower than their Rademacher complexity. This proves the existence smaller coresets than those achievable by random sampling. 
New results for coresets for kernel density estimation, matrix covariance approximation, and logistic regression are presented both as examples of for providing mechanisms to compute the Komlos complexity of other classes.
For all of the above we match the state of the art or improve on it.
This makes an explicit connection between low discrepancy, streaming algorithms, coresets, and learnability. 
%We also asymptotically improve on the generic merge-reduce framework for creating mergeable sketches for all the above problems. 
\end{abstract}

@@

\el{I need to rewrite this section.}
In many machine learning and sketching problems our goal is often to approximate the sum (or expectation) of functions.
Specifically, function of the form $F(q) = \sum_{i=1}^{n} f(x_i, q)$ where $x_i \in \mathcal X$ are either training examples or stream items and $q \in \mathcal Q$ is either the model parameters or a query from a possible set $\Q$ which is known in advance. For simplicity and throughout this manuscript we will assume $f:\X\times\Q\rightarrow [0,1]$.
The goal is to produce weights $w$ with at most $k \ll n$ non-zeros such that $\sum_{i=1}^{n}w_i f(x_i,q) := \tilde F(q)$ approximates $F(q)$.
Approximation here means that $|\tilde F(q)  - F(q)| \le \eps n$ either for all possible queries $q \in \mathcal Q$ simultaneously or for every fixed $q$ with probability at least $1-\delta$. 
There are more complicated formulations such as weak coresets which we will not touch upon in this manuscript.

@@

\section{The Complexity of Analytic Functions of Dot Products}

We are now ready to apply Banaszczyk's theorem. 
There exist signs $\sigma_i$ such that $\psi  = \sum_i \sigma_i \psi(x_i) \in C \mathcal K$.
Since $\psi_k = \sum_i \sigma_i x_i^{\otimes k}/\sqrt{k \log^2{k}}$ we get that $\max_k \|\sum_i \sigma_i  x_i^{\otimes k}\|_{T_k} \le \sqrt{d k \log^{3}(k)}$
\end{proof}

\begin{lemma} \label{lem:komlos anl}
Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion. The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq 1$, is bounded by
\[
K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}\right)
\]
For general $\|q\| \leq R$ we get
\[
K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}\right)
\]
\end{lemma}
\begin{proof}
The proof follows from combining the above.
$$
\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \cdot \|q\|^k
$$
By Lemma \ref{uc} we can find signs $\sigma$ such that 
$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
\end{proof}

\begin{theorem}\label{analitic1}
Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq R$, has Komlos complexity of $O(\sqrt{d}/m)$. 
\end{theorem}
\begin{proof}
Recall that for analytic functions $f$ we have $\left| \frac{d^k f}{dz^k}(z) \right|  \leq C^{k+1} k! $
for some constant $C$. Considering the taylor expansion of $f$ near zero. For $R < 1/C$, the sum
$ \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)} \leq C \sum_k  (CR)^k \sqrt{ k\log^3(k)}$
corresponding to Lemma~\ref{lem:komlos anl} converges to a constant. The result follows.
\end{proof}

\begin{corollary}
The Komlos complexity of the Logistic function $f(\ip{q,x}) = \log(1+\exp(\ip{q,x}))$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$.
\end{corollary}

\begin{corollary}
The Komlos complexity of the covariance function $f(\ip{q,x}) = \ip{q,x}^2$ in dimension $d$, for $\|q\| \leq 1$ is $O(\sqrt{d}/m)$. This gives coresets for matrix column subset selection such that $\|XX^T - \tilde X \tilde X^T\| \le \eps n$ where $\tilde X$ contains $O(\sqrt{d}/\eps)$ rescales columns of the matrix $X$.
\end{corollary}

\begin{theorem}
Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq \sqrt{R}$, has Komlos complexity of $O(\sqrt{d}/m)$. 
\end{theorem}
\begin{proof}
By transforming $x$ to $\tilde{x} = (x, \|x\|^2, 1)$ and $q$ to $\tilde{q} = (-2q, 1, \|q\|^2)$ we get $\ip{\tilde{x},\tilde{q}} = \|x-q\|^2$. Moreover, $\|q\| \le \sqrt{R}$ gives $\|\tilde q\| \le R$. The result follows from applying Theorem~\ref{analitic1} to $f(\ip{ \tilde q, \tilde x}) = f(\|q-x\|^2)$ apply for functions of $\|q-x\|^2$.
\end{proof}

\begin{corollary}
The Komlos complexity of the Gaussian kernel in dimension $d$ is $O(\sqrt{d}/m)$.
This improves upon the recent result of \el{\cite{??}} by proving the existence of $\eps$ approximation corsets of size $\sqrt{d}/\eps$ for Gaussian kernel density.
This resolves the open problem raised by \el{\cite{??}} and matches their lower bound.   
\end{corollary}
%\end{proof}

From section \ref{} we know that the Komlos complexity of the Gaussian kernel is $K_m = O(\sqrt{d}/m)$. Here, we show that for any positive kernel $K_m = O(1/\sqrt{m})$. This bound is better when $d > m$. More importantly though, there is a very simple, intuitive, and deterministic algorithm for computing the signs $\sigma$. 
Given a collection of data points $X = x_1,\ldots, x_n$ in $\R^d$ the density function $f: \R^d \rightarrow \R$ of a point $q$ is defined as 
$$ f(q) = \sum_{i=1}^{n} K(x_i,q) $$
Here, $K$ is a \emph{positive definite kernel} function, typically based on the distance between $x,y$. The most frequent examples include
$$ K(x,q) = \exp(- \|x-y\|_2^2/\lambda^2)\;\;\; K(x,q) = \exp(- \|x-q\|/\lambda) \; \mbox{and}\;\;\; K(x,y) = (1+\|x-q\|/_2^2/\lambda^2)^{-1}$$
where $\lambda$ is a scaling parameter. For simplicity, we assume that $K(x,x) \leq 1$ for all data points. Notice that for any kernel based on distance we have $K(x,x)=1$ exactly for all $x \in \R^d$.

Using our framework, we need to bound $K_m = \frac{1}{m}\sum_{i=1}^m \sigma_i K(x_i,q)$. For any kernel $K$ there exist a mapping $\phi: \R^d \to {\cal V}$ to an inner product space $\cal V$ such that 
$$ K(x,q) = \ip{\phi(x), \phi(q)} $$
Using this function $\phi$ our objective function becomes
\[
\sum_{i=1}^m \sigma_i K(x_i,q) = \sum_{i=1}^m \sigma_i \ip{\phi(x_i), \phi(q)} =  \ip{ \sum_{i=1}^m \sigma_i \phi(x_i), \phi(q)} \leq  \|\phi(q)\| \cdot \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| %\leq \left\|  \sum_{i=1}^m \sigma_i \phi(x_i) \right\| 
\]
This upper bound allows us to find values for $\sigma_i$ which bound $K_n$ using a simple algorithm.
Set $\sigma_1 = 1$. Then for $i=2,\ldots,m$ set $\sigma_i = -\operatorname{sign} (\sum_{j=1}^{i-1}\sigma_j  K(x_j, x_i))$.
We will show by induction that $\| \sum_{j=1}^i \sigma_j \phi(x_j) \|^2 \le \sum_{j=1}^i \|\phi(x_j)\|^2$ for all $i$.
This is trivially true for $i=1$. 
Assume by induction that $\| \sum_{j=1}^{i-1} \sigma_j \phi(x_j)\|^2 \le \sum_{j=1}^{i-1} \|\phi(x_j)\|^2$.

\begin{eqnarray*}
\| \sum_{j=1}^{i}\sigma_j \phi(x_j)\|^2 &=& \|\sum_{j=1}^{i-1}\sigma_j \phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\langle \sum_{j=1}^{i-1}\sigma_j \phi(x_j), \sigma_i \phi(x_i)\rangle \\
&\le& \sum_{j=1}^{i-1} \|\phi(x_j)\|^2 + \|\phi(x_i)\|^2 + 2\sigma_i \sum_{j=1}^{i-1}\sigma_j K(x_j, x_i) \mbox{\;\;\; by the induction assumption}\\ 
&=& \sum_{j=1}^{i} \|\phi(x_j)\|^2 - 2|\sum_{j=1}^{i-1}\sigma_j K(x_j, x_i)| \le \sum_{j=1}^{i} \|\phi(x_j)\|^2
\end{eqnarray*}
This completes the proof that $\| \sum_{j=1}^{m}\sigma_j \phi(x_j)\| \le \sqrt{\sum_{j=1}^{i} \|\phi(x_j)\|^2} \le \sqrt{m}$ for our choice of values for $\sigma$ and shows that the Komlos complexity of any positive kernel is $O(1/\sqrt{m})$.

Using the framework above this provides a deterministic coreset construction for kernel density estimation of size $O(1/\eps^2)$ such that $\forall \;q\;\; |\tilde f(q) - f(q)| \le \eps n$. This matches, and greatly simplifies, the results achieved by \cite{DBLP:conf/soda/PhillipsT18} and \cite{DBLP:journals/corr/abs-1802-01751}.

\appendix

\section{Proofs for Streaming Coresets}

@@

\zk{need to finish the analysis for the above $K_k$.}
\end{proof}

\section{Table of Complexities for Common Classes}

@@

To invoke Banaszczyk's theorem here we set $x_i \in \R^{d_1d_2}$ to be the flattening of $X_i$ into a vector by concatenating its rows. 
Let $\mathcal K$ be the set of vectors in $\R^{d_1d_2}$ whose stacking (the inverse of flattening) results in a matrix whose spectral norm is less then $c\sqrt{d_1 + d_2}$.
More accurately $\mathcal K = \{x  \in \R^{d_1d_2} |\;\; ||\operatorname{stack}(x)||_2 \le c\sqrt{d_1+d_2}\}$. 
Due to $\operatorname{stack}$ being linear it is obvious that $\mathcal K$ is convex. 
Moreover $\Pr[g \in \mathcal K] \ge 1/2$ due to standard results on the operator norm of random Gaussian matrices (see Theorem~\ref{thm:random tensor}).
Banaszczyk's theorem says that there exist signs $\sigma_i$ such that $\sum \sigma_i \operatorname{flatten}(X_i) \in C \mathcal K$.
In other words $\| \sum \sigma_i X_i\| = \| \operatorname{stack}( \sum \sigma_i \operatorname{flatten}(x_i x_i^T)) \| \le C \sqrt{d}$.

The algorithm for finding the signs above is, unfortunately, not as simple as with kernels. 
In fact, Banaszczyk's theorem was not constructive and a matching algorithms is a very recent breakthrough result by Bansal, Dadush, Garg, and Lovett \cite{DBLP:conf/stoc/BansalDGL18}.

@@

\section{Streaming Graph Approximation}
Streaming graphs have received a lot of attention in the last several years \zk{cite something here \cite{}}. 
In the standard setting, the edges of a graph $G(V,E)$ are given to an algorithm one ofter the other in arbitrary order.
Here we show how to approximate all quadratic forms $\sum_{(i,j) \in E} (q_i - q_j)^2$ where the values $q$ are not known in advance.
Let $L_e$ be the graph Laplacian of the edge $e$. More accurately, $L_e(i,i) = L_e(j,j) = 1$ and  $L_e(i,j) = L_e(j,i) = -1$ and all other values are zeros.
Then, $\sum_{(i,j) \in E} (q_i - q_j)^2 = q^T \sum_{e \in E}L_e q = q^T L q$. 
In this formulation, this problem reduced to that of row (column) subset selection. 
Note that $L_e = v_ev_e^T$ where $v_e(i) = 1$, $v_e(j)=-1$ and zero else.
Applying the results of the last section we get a streaming mergeable algorithm of approximating graph quadratic forms.
The number of retained edges in the coreset $E'$ is $|E'| = O(\log^{2}(n) \sqrt{n}/\eps)$ and it guaranties that 
$|\sum_{(i,j) \in E} (q_i - q_j)^2  - c \sum_{(i,j) \in E'} (q_i - q_j)^2| \le \eps n$ for all unit norm vectors $q$.
